Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-12 manuscript/manuscript.tex
updated figures

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}

@@

\begin{figure}
  \centering
  \includegraphics[]{figures/figure-3.pdf}

@@

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1-revision.pdf}

@@

\begin{figure}
  \centering
  \includegraphics[]{figures/figure-3-revision.pdf}

@@

We conducted extensive simulations to understand how temporal covariance,
$G(t)$, and convergence correlations behave under (1) different fitness models,
(2) different trait architectures (e.g. varying levels of $V_A$ for fitness and
the number of sites affecting fitness), (3) background selection, (4) and
